Long name of the paper

### 2018-05-30 anzjs2018/anzjs2018.tex
few words

\documentclass[times, doublespace]{anzsauth}
\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage{lineno}
\usepackage{lipsum}
\usepackage[UKenglish]{isodate}

@@

\keywords{particle filter; Kalman filter; transit modeling;
          transit networks; statistical computing}

@@

Overview of the history, problem, proposed solution I guess...

@@

Before we can usefully model buses in real-time, 
we need to construct a \emph{transit network}, 
consisting of \emph{intersections} (nodes),
connected by \emph{road segments} (edges).
In this way, each \emph{route} 
(a journey taken by a transit vehicle, from an origin to a destination by a fixed path)
can be represented as a sequence of road segments,
each of which we will model as vehicles travel along them (see section~\ref{sec:kf}).

@@

>>>>

\documentclass[times, doublespace]{anzsauth}
\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage{lineno}
% \usepackage{lmodern}
\usepackage{lipsum}
\usepackage[UKenglish]{isodate}

\input{../glossary.tex}

@@

\keywords{particle filter; Kalman filter; transit modeling;
          transit networks; statistical computing; applications}

@@

Bus arrival-time prediction is far from a novel concept: 
ever since the first vehicle tracking technology was implemented
in transit vehicles in the late 1980's, 
real-time models have been implemented to provide \gls{rti} for commuters.
The simplest form of this is, the \gls{eta}
(usually displayed as \emph{minutes until arrival}),
was implemented in {{region}} by \cite{Wall99analgorithm} 
using their proposed \gls{kf} algorithm.
In their work, they used historical data to obtain \glspl{eta}.

Over the years, advances in computing power have enabled new
modeling approaches,
such as support vector machines \citep

@@

Before we can usefully model buses in real-tim{}e, 
we need to construct a \emph{transit network},
consisting of \emph{intersections} (nodes)
connected by \emph{road segments} (edges).
In this way, each \emph{route} 
(a journey taken by a transit vehicle, from an origin to a destination by a fixed path)
can be represented as a sequence of road segments,
each of which we model as vehicles travel along them (see section~\ref{sec:kf}).

@@

\bibliographystyle{anzsj}
\bibliography{../reflist.bib}
